HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
preliminary discussion

\section{Preliminary Discussion}

>>>>

\section{Preliminary Discussion}
While the differences between speed and accuracy are statistically insignificant, a discussion can still take place. The stacked interface was perceived by the participants to be faster, which held when examining the data. This is inline with previous literature like the work of Warr and Chi [7]. However, this begs the question: why is stacked interface perceived as quicker? It’s possible this is due to the fact that the motion of the cards is toward the user rather than down. In addition, with the stacked interface the user can control the sensitivity of the scroll by scrolling from higher up on the screen. This allows users to more quickly traverse a long list of apps at the cost of some granularity of motion.

A stacked interface may only provide nominal speed and accuracy increases when compared to a non-stacked interface. As a result, future research should focus on alternate means to facilitate app switching as opposed to the conventional historical listing of applications. Throughout all mobile app switching interfaces, almost exclusively, the “most recently used” rule is used to sort applications in the list. Future research should look into using different sorting schemes to predict which application a user will need next. Perhaps machine learning could be applied to predict what application may be used next as is being tested in Apple’s new recents menu.

One limitation of our participant group was their familiarity with the two operating systems. From the starting survey 9 participants were mostly familiar with Lollipop whereas only 3 were mostly familiar with KitKat. Another limitation is that the study only tested one model of phone with stock Android. The real consumer landscape for Android contains many different sized phones running various modified versions of Android.

Overall, the study shows that the differences between the two interfaces are statistically insignificant for accuracy and speed. The stacked card interface was rated as generally more pleasant and quicker, which could be a reason Android changed the interface.
